---
title: "My Fancy Presentation"
author: "Chad"
date: "January 24, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide
Some Content

## My Title
- Bullet 1
- Bullet 2
1. Item a
2. Item b

## My New Slide 2
Plain Text

*italicized text*

**bold text**

'for(i)

## My New Rcode Run
```{r, comment=""}
head(mtcars)

```

## My New Rcode Run 2
```{r, comment=""}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="MPG")

```
Figure 1: As weight increases your MPG will decrease

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

